\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{9}
  \bibitem{fu11} H. Fu and R. G. Clapp, \emph{Eliminating the memory
    bottleneck: an FPGA-based solution for 3d reverse time migration,}
    in Proceedings of the 19th ACM/SIGDA international symposium on Field
    programmable gate arrays, 2011, pp. 65-74.

  \bibitem{herb11} Herb Sutter, \emph{The Free Lunch Is Over: A Fundamental
    Turn Toward Concurrency in Software,} Dr. Dobb's Journal, 30(3), March
    2005. Retrieved 21 November 2011.

  \bibitem{yoon03} K. Yoon, C.Chin, S. Suh, L. Lines, and S. Hong.
    \emph{3D Reverse-time Migration Using the Acoustic Wave Equation:
    An Experience with the SEG/EAGE Data Set.} The Leading Edge, 22(1):38-41,
    2003.

  \bibitem{moore}
    \emph{Moores law, Wikipedia, the free encyclopedia} [online],
    http://en.wikipedia.org/wiki/Moore's\_law.

  \bibitem{shafiq} M. Shafiq, M. Pericas, N. Navarro, and E. Ayguade,
    \emph{A Streaming Based High Performance FPGA Core for 3D Reverse
    Time Migration.}

  \bibitem{river} G. Rivera and C. Tseng.
    \emph{Tiling Optimizations for 3D Scientific Computations.}
    In Proc. Supercomputing, 2000.

  \bibitem{navarro} M. Shafiq, M. Pericas, R. de la Cruz, M. Araya-Polo,
    N. Navarro, and E. Ayguade.
    \emph{Exploiting Memory
    Customization in FPGA for 3D Stencil Computations.}
    In Proc. International Conference on Field
    Programmable Technology (FPT), pages 38-45, 2009.

  \bibitem{garey} W. Spotz and G. Carey.
    \emph{A High-Order Compact Formulation for the 3D Poisson Equation.}
    Numerical Methods for Partial Differential Equations, 1996.

  \bibitem{top500}
    \emph{Top500 super computer sites - November 2012} [online],
    http://www.top500.org

  \bibitem{chin}K. Yoon, C.Chin, S. Suh, L. Lines, and S. Hong.
    \emph{3D Reverse-time Migration Using the Acoustic Wave
      Equation: An Experience with the SEG/EAGE Data
    Set. }
    The Leading Edge, 22(1):38–41, 2003.
  \bibitem{fpgaintro}
    J. Serrano,
    \emph{DIGITAL SIGNAL PROCESSING USING FIELD PROGRAMMABLE GATE ARRAYS,}
    Proceedings of BIW08, pp. 29-38, 2008.

  \bibitem{fpgaug}
    Xilinx Inc,
    \emph{Xilinx UG331 Spartan-3 Generation FPGA User Guide}

  \bibitem{migration} Baysal, E., Kosloff, D. D. and Sherwood, J. W. C.,
    \emph{Reverse time migration}, GEOPHYSICS, Soc. of Expl.
    Geophys., Vol. 48, p 1514-1524, 1983

  \bibitem{wave}Dablain, M. A.,
    \emph{The application of high-order
    differencing to scalar wave equation.} GEOPHYSICS, Soc. of
    Expl. Geophys., Vol. 51, p 54-66,1986

  \bibitem{shaped} Gwarek, W.K.. {Analysis of Arbitrarily Shaped Two-
      Dimensional Microwave Circuits by Finite-Difference
    Time-Domain Method,}
    IEEE Trans. Microwave Theory and Techniques, vol. 36, no. 4, pp.738-744.

  \bibitem{max_white_paper}
    Maxeler Technologies,
    \emph{MaxCompiler White Paper} [online],
    https://www.maxeler.com/media/documents/MaxelerWhitePaperMaxCompiler.pdf

  \bibitem{rtm}
    PGS Techlink,
    \emph{Reverse Time Migration} [online],
    http://www.pgs.com/upload/188525/techlink40\_rtm\_sm.pdf

  \bibitem{rtm_psdm}
    M. H. Karazincir and C. M. Gerrard,
    \emph{Explicit high-order reversetime pre-stack depth migration,}
    in 76th Annual International Meeting, SEG, Expanded Abstracts, 2006,
    vol. 25, pp. 2353-2357.

  \bibitem{maxcompiler_tutorial}
    \emph{MaxCompilerKernel Compiler Tutorial} [commercial]

\end{thebibliography}
